Distributed Behavior in a Fluid Analogy Architecture

### 2017-12-01 papers/draft.tex
Adds draft.tex, an organized paper draft to be..

\title{The Distributed Nature of Copycat..? (WIP)}
\author{Lucas Saldyt, Alexandre Linhares}

@@

\begin{abstract}
    We investigate the distributed nature of computation in a FARG architecture, Copycat. 
    One of the foundations of those models is the \emph{Parallel Terraced Scan}--a psychologically-plausible model that enables a system to fluidly move between different modes of processing.  
    Previous work has modeled decision-making under Parallel Terraced Scan by using a central variable of \emph{Temperature}. 
    However, it is unlikely that this design decision accurately replicates the processes in the human brain.

    Additionally, Copycat and other FARG architectures have incredible high rates of unscientific inquiry.
    Specifically, Copycat uses many undocumented formulas and magic numbers, some of which have been parameterized to fix particular problems at the expense of performing worse on others.
    This paper aims to add a framework for conducting so-called "Normal" science with Copycat, in the hopes of making our findings more concrete.

\end{abstract}

\section{Introduction}

    This paper stems from Mitchell's (1993) and Hofstadter \& FARG (1995). The goals of this project are twofold:

    Firstly, we focus on effectively simulating intelligent processes through increasingly distributed decision-making.
    ...
    Written by Linhares:
    The Parallel Terraced Scan is a major innovation of FARG architectures. 
    It corresponds to the psychologically-plausible behavior of briefly browsing, say, a book, and delving deeper whenever something sparks one's interest. 
    This type of behavior seems to very fluidly change the intensity of an activity based on local, contextual cues. 
    It is found in high-level decisions such as marriage and low-level decisions such as a foraging predator choosing whether to further explore a particular area. 
    Previous FARG models have used a central temperature T to implement this behavior. 
    We explore how to maintain the same behavior while distributing decision-making throughout the system.
    ...
    Specifically, we begin by attempting different refactors of the copycat architecture.
    First, we experiment with different treatments of temperature, adjusting the formulas that depend on it
    Then, we experiment with two methods for replacing temperature with a distributed metric, instead.
    First, we remove temperature destructively, essentially removing any lines of code that mention it, simply to see what effect it has.
    Then, we move toward a surgical removal of temperature, leaving in tact affected structures or replacing them by effective distributed mechanisms.

    Secondly, we focus on the creation of a `normal science' framework in FARG architectures. 
    By `normal science' we use the term created by Thomas Kuhn--the collaborative enterprise of furthering understanding within a paradigm. 
    Today, "normal science" is simply not done on FARG architectures (and on most computational cognitive architectures too... see Addyman \& French 2012). 
    Unlike mathematical theories or experiments, which can be replicated by following the materials and methods, computational models generally have dozens of particularly tuned variables, undocumented procedures, multiple assumptions about the users computational environment, etc. 
    It then becomes close to impossible to reproduce a result, or to test some new idea. 
    This paper focuses on the introduction of statistical techniques, reduction of "magic numbers", improvement and documentation of formulas, and proposals for effective human comparison.

    We also discuss, in general, the nature of the brain as a distributed system.
    While the removal of a single global variable may initially seem trivial, one must realize that copycat and other cognitive architectures have many central structures.
    This paper explores the justification of these central structures in general.
    Is it possible to model intelligence with them, or are they harmful?
    ...

@@

>>>>

\title{Distributed Behavior in a Fluid Analogy Architecture}
\author{Lucas Saldyt, Alexandre Linhares}

@@

\begin{abstract}
    [Write Abstract]
\end{abstract}

\section{Introduction}
\section{Theory}
    \subsection{Normal Science}
        \subsubsection{Scientific Style}
        \subsubsection{Scientific Testing}
    \subsection{Distribution}
        \subsubsection{Von Neumann Discussion}
        \subsubsection{TODO}
\section{Methods}
    \subsection{Formula Adjustments}
        \subsubsection{Temperature Probability Adjustment}
        \subsubsection{Temperature Calculation Adjustment}
        \subsubsection{Temperature Usage Adjustment}
    \subsection{Chi \^ 2 Distribution Testing}
\section{Results}
    \subsection{Chi \^ 2 Table}
\section{Discussion}
    \subsection{Distributed Computation Accuracy}
    \subsection{Prediction}

@@

    \break
    .....
    \break

    The calculation for temperature in the first place is extremely convoluted (in the Python version of copycat).
    It lacks any documentation, is full of magic numbers, and contains seemingly arbitrary conditionals. 
    (If I submitted this as a homework assignment, I would probably get a C. Lol)

    Edit: Actually, the lisp version of copycat does a very good job of documenting magic numbers and procedures.
    My main complaint is that this hasn't been translated into the Python version of copycat.
    However, the Python version is translated from the Java version..
    Lost in translation.

    My goal isn't to roast copycat's code, however.
    Instead, what I see is that all this convolution is \emph{unnecessary}.
    Ideally, a future version of copycat, or an underlying FARG architecure will remove this convolution, and make temperature calculation simpler, streamlined, documented, understandble.
    How will this happen, though?

    A global description of the system is, at times, potentially useful.
    However, in summing together the values of each workspace object, information is lost regarding which workspace objects are offending.
    In general, the changes that occur will eventually be object-specific.
    So, it seems to me that going from object-specific descriptions to a global description back to an object-specific action is a waste of time.

    I don't think that a global description should be \emph{obliterated} (removed 100\%).
    I just think that a global description should be reserved for when global actions are taking place.
    For example, when deciding that copycat has found a satisfactory answer, a global description should be used, because deciding to stop copycat is a global action.
    However, when deciding to remove a particular structure, a global description should not be used, because removing a particular offending structure is NOT a global action.

    Summary: it is silly to use global information to make local decisions that would be better made using local information (self-evident).

    Benefits of using local information to make local decisions:

    Code can be truly distributed, running in true parallel, CPU-bound.
    This means that copycat would be faster and more like a human brain.
    Specific structures would be removed based on their own offenses.
    This means that relvant structures would remain untouched, which would be great!
    Likely, this change to copycat would produce better answer distributions testable through the normal science framework.

    On the other hand (I've never met a one-handed researcher), global description has some benefits.
    For example, the global formula for temperature converts the raw importance value for each object into a relative importance value for each object.
    If a distributed metric was used, this importance value would have to be left in its raw form.
